manuscript

### 2019-02-01 manuscript/manuscript.Rmd
Update manuscript.Rmd
Inserted text pertaining to extract_homologs2 output files added to text

Our analysis for immunity-related genes largely follows the same workflow as used for Hbs, but instead were processed through the Extract_Homologs2 script used in [@tassia2017toll] (available at https://github.com/mtassia/Homolog_identification). Target proteins are available in Table S#. Importantly, the Extract_Homologs2 script identifies unique protein sequences within an animo acid dataset which fall within user-defined domain architecture criteria (Table S#+1). Due to this stringency, the pipeline identifies the complement of unique proteins for any target family, not the number of synonymous genes encoded in a genome.  Full amino acid sequences for TLRs were placed in a phylogenetic context using the bioinformatic workflow delineated above for Hbs.

>>>>

Our analysis for immunity-related genes largely follows the same workflow as used for Hbs, but instead were processed through the Extract_Homologs2 script used in [@tassia2017toll] (available at https://github.com/mtassia/Homolog_identification). Target proteins are available in **Table S#**. Importantly, the Extract_Homologs2 script identifies unique protein sequences within an animo acid dataset which fall within user-defined domain architecture criteria (**Table S#, same as above**). Due to this stringency, the pipeline identifies the complement of unique proteins for any target family, not the number of synonymous genes encoded in a genome. Major output files produced by this pipeline are available as **supplementary files X-(X+3)**. Full amino acid sequences for TLRs were placed in a phylogenetic context using the bioinformatic workflow delineated above for Hbs.
